---
title: "My first notebook"
author: "Chandan Kumar Pandey"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

# Activity uno

## Advantage of R Markdown

### Question 1:- Does the number of hours students study impact their grades? 

#### Introduction 

You can write your introduction here

#### Method (Hypothetical)

We conducted a survey in schools of Bangalore North Taluk to understand the impact of the number of hours of study on student final scores. Student's parents were interviewed during parent-teacher meetings (PTA) to collect data on number of hours the child. Further from the school records, we collected overall final grades. 
To assess the impact of study time and course taken on the overall grades, we fitted a linear regression model with the number of hours as the independent variable and number of courses enrolled in and marks are response variable;($marks=\beta_1*Number of course +\beta_2 * Hours study + \epsilon$), where $\epsilon~N(0,1)$ .
All analyses were performed in R statistical software (@boud1989quantitative) `r R.Version()$version.string`.

#### Results

```{r data load and prim ana, include=F,echo=F,warning=FALSE}
library(dplyr,warn.conflicts = F)
##loading the dataset into the R
student_marks<-read.csv("./Data/Student_Marks.csv",header = T)
student_marks$Marks <- log(student_marks$Marks)
range_study <- range(student_marks$time_study)%>%round(2)
range_marks <- range(student_marks$Marks)%>%round(2)
```

A total of `r nrow(student_marks)` student records were collected, with the number of courses students were enrolled in ranging between `r min(student_marks$number_courses)` and `r max(student_marks$number_courses)`. Based on parents' interviews, on average, students studied for `r round(mean(student_marks$time_study),2)` hours per day (ranging from `r range_study[1]` to `r range_study[2]` per day). Further, the average mark scored was `r round(mean(student_marks$Marks),2)` in log scale, ranging from `r range_marks[1]` to `r range_marks[2]`..

```{r linear model, include=T,echo=T,warning=F}
model <- lm(Marks~number_courses+time_study,data = student_marks)
anova_table <- anova(model)%>%as.data.frame()%>%round(3)
model_summary <- summary(model)
summary_table <- model_summary$coefficients%>%as.data.frame()%>%round(3)
rownames(summary_table) <- c("Intercept","Courses enrolled-in","Per day hours of study")
```

In our model, the number of courses(`r anova_table[1,1]`,`r anova_table[1,4]`,___p<0.005___ ) and study times (`r anova_table[2,1]`,`r anova_table[2,4]`,___p<0.005___ )were significant in explaining the student's grades in the final examination (__Table 1__). Overall, our model was able to explain `r round(summary(model)$adj.r.squared*100,2)`% of the variation in the marks of students. With the increase in each course, the student average grades improved by `r paste(summary_table[1,1],"(", summary_table[1,2],")",sep = "")`. Similarly, each extra hour of study will increase the score by a factor of `r paste(summary_table[2,1],"(", summary_table[2,2],")",sep = "")` (Table 2, Fig1) 

```{r tables1 in latex,include=TRUE,echo=F,eval=knitr::is_latex_output(),warning=FALSE}
library(knitr)
library(kableExtra)
## preparing the tables
## Table 1 anova table

kbl(anova_table, booktabs = T,caption = "Table1: Annova output of the model") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r tables1 in html,include=TRUE,echo=F,eval=!knitr::is_latex_output(),warning=FALSE}
library(knitr)
## preparing the tables
## Table 1 anova table
anova_table <- anova(model)%>%as.data.frame()%>%round(3)
kable(anova_table,caption = "Table1: Annova output of the model")
## one can style this table using another package called flextable
```

```{r addition table 2 latex,include=TRUE,echo=F,eval=knitr::is_latex_output(),warning=F}
library(knitr)
library(kableExtra)
## preparing the tables
## Table 1 anova table
kbl(summary_table, booktabs = T,caption = "Table2: model summary") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r tables1 in table 2 word,include=T,echo=F,eval=!knitr::is_latex_output(),warning=FALSE}
library(knitr)
## preparing the tables
## Table 1 anova table
kable(summary_table,caption = "Table2: model summary")
## one can style this table using another package called flextable
```

```{r graphs, include=T,echo=F,warning=F,fig.cap="Student performace in relation to number of hours study and courses enrolled in",fig.height=4,fig.width=6}
library(ggplot2,warn.conflicts = F)
predicted_value<-predict.lm(model,interval = "confidence")%>%as.data.frame()
student_marks<-cbind(student_marks,predicted_value)
plot <- ggplot(data = student_marks, aes(x=time_study,y=Marks,col=as.factor(number_courses)))
plot+geom_point()+
  geom_line(aes(y=fit))+
  geom_ribbon(aes(ymin=lwr,ymax=upr),alpha=0.05)+
  theme_bw()+
  labs(
        x="Study hours per day",
    y="Marks scored (log)"
  )
```


#### Discussion

1. Our study align with words of elder that with more study we can get good grades
2. It was surprising that several courses also increased the overall mark. This may be due      to the following reasons
   * Generally, people who study more take more courses.
   * The average of many subjects compensates for few bad results. 
   
